A sensor grid approach for large scale acoustic monitoring

### 2017-06-22 paper/article.tex
addition in intro

In our application setting, the requirements are the following. First,  the number of sensor nodes shall be extended as needed without having to change the hardware and software architecture, \textit{i.e.} the approach shall be scalable. Second, the nodes shall be energy efficient in order ot ease the deployment of the sensors grid to the desired topology, ideally autonomous. Third, the data transfer used to transmit the data from the sensor to the storage and processing servers shall be designed with care in order to ensure the privacy of the citizen. Lastly, the data stored shall be as rich as possible while retaining a low bitrate for efficient transmission and storage

@@

However, transmitting the raw audio through the network has several disavantages, in terms of required bandwidth, storage capabilities and privacy. Thus, for transmission from the sensors to the storage unit, the data needs to be encoded in an efficient way. Also, as the data is transmitted using the network and stored, one must ensure that the intelligibility of potential speech utterances is lost during the coding process, in order to ensure the privacy of the citizens.

>>>>

In our application setting, the requirements are the following. First,  the number of sensor nodes shall be extended as needed without having to change the hardware and software architecture, \textit{i.e.} the approach shall be scalable. Second, the nodes shall be energy efficient in order ot ease the deployment of the sensors grid to the desired topology, ideally autonomous. Third, the encoding scheme used to transmit the data from the sensor to the storage and processing servers shall be designed with care in order to ensure the privacy of the citizen. Lastly, the data stored shall be as rich as possible while remaining a low bitrate for efficient transmission and storage.

@@

However, transmitting the raw audio through the network has several disavantages, in terms of required bandwidth, storage capabilities and privacy. Thus, for transmission from the sensors to the storage unit, the data can be encoded in a more efficient way than lossy audio encoding standards \cite{pan1995tutorial} as the audio signal is not mandatory for the computation of the acoustic indicators and the features needed for event recognition. Also, as the data is transmitted using the network and stored, one must ensure that the intelligibility of potential speech utterances is lost during the coding process, in order to ensure the privacy of the citizens.
